The limits of self commitment and private paternalism \thanks{}

### 2022-11-12 donde.tex
who makes mistakes based on ml models on ps and hte
start analysis on asl and asb

\title{The limits of self-commitment and private paternalism \thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Francis DiTraglia, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Frank DiTraglia   \thanks{Seira: ITAM/MSU, enrique.seira@gmail.com (corresponding author); McIntosh:  University of California San Diego, ctmcintosh@ucsd.edu; Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx; DiTraglia: Oxford, frank@ditraglia.com} }
\date{This draft:  \today \\[2 cm]}

@@

The key insight can be read directly from \eqref{eq:potentialTreatments} and \eqref{eq:potentialOutcomes}. Viewing $Z_i$ as an instrumental variable, our design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.\footnote{For a full derivation, see Appendix ???.} The first of these compares $Z_i=0$ to $Z_i = 2$. For each individual with $Z_i = 0$ we have $D_i = 0$ and observe $Y_{i0}$. For those with $Z_i = 2$ we have $D_i = C_i$ and observe $(1 - C_i) Y_{i0} + C_i Y_{i1}$. This is identical to a ``randomized encouragement'' design in which treatment is only available to those who are encouraged: $Z_i = 2$. Under this interpretation, those with $C_i = 1$ are ``the compliers'' and it follows that 
\begin{equation}
\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)-\mathbbm{E}(D_i|Z_i=0)} = 
\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} = \mathbbm{E}(Y_{i1} - Y_{i0}|C_i = 1)
\label{eq:ToT}
\end{equation}
since $\mathbbm{E}(D_i|Z_i=0)=0$ by \eqref{eq:potentialTreatments}.

@@

\begin{figure}[H]
    \caption{Effect of CATE benefit vs predicted take-up}
    \label{HTE_vs_propensity}
    \begin{center}
    \begin{subfigure}{0.475\textwidth}
        \caption{Effective APR}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_apr.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Repayment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_des.pdf}
    \end{subfigure}
     \begin{subfigure}{0.475\textwidth}
        \caption{Default}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_def.pdf}
    \end{subfigure} 
    \end{center}
     \scriptsize   This figure asks whether it is the case that people with larger causal benefits from the Forced Commitment contract would be more likely to select that contract. To do this we proceed in two steps. First we estimate a flexible model of take-up of the commitment-fee contract \textit{in the choice arm} using gradient boosting classification, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$. We extrapolate this model to clients in the Forced Commitment arm to estimate what would they have chosen if we had given them choice. We plot $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins. The Y-axis plots the heterogeneous treatment effects of the (a) effective APR (in the positive scale) and (b) repayment, averaged for the respective x-axis bin. Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it. 
          %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
\end{figure}

@@

\begin{figure}[H]
    \caption{Negative selection on treatment effects}
    \label{benefit_vs_choice_cdf}
    \begin{center}
    \begin{subfigure}{0.475\textwidth}
        \caption{Effective APR benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_apr.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Repayment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_des.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Default}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_def.pdf}
    \end{subfigure}
    \end{center}
     \scriptsize    CDF of the heterogeneous treatment effect for choosers vs non-choosers. The dotted line below indicates the points where the difference in the distributions is significant.  Instead of a single global null hypothesis (that the two CDFs are identical), there is a continuum of individual null hypotheses of CDF equality at each point. This methodology was proposed by \cite{GOLDMAN2018143}.
          %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
\end{figure}

>>>>

\title{The limits of self-commitment and private paternalism \thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Frank DiTraglia   \thanks{Seira: ITAM/MSU, enrique.seira@gmail.com (corresponding author); McIntosh:  University of California San Diego, ctmcintosh@ucsd.edu; Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx; DiTraglia: Oxford, frank@ditraglia.com} }
\date{This draft:  \today \\[2 cm]}

@@

The key insight can be read directly from \eqref{eq:potentialTreatments} and \eqref{eq:potentialOutcomes}. Viewing $Z_i$ as an instrumental variable, our design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.\footnote{For a full derivation, see \hl{Appendix ???}.} The first of these compares $Z_i=0$ to $Z_i = 2$. For each individual with $Z_i = 0$ we have $D_i = 0$ and observe $Y_{i0}$. For those with $Z_i = 2$ we have $D_i = C_i$ and observe $(1 - C_i) Y_{i0} + C_i Y_{i1}$. This is identical to a ``randomized encouragement'' design in which treatment is only available to those who are encouraged: $Z_i = 2$. Under this interpretation, those with $C_i = 1$ are ``the compliers'' and it follows that 
\begin{equation}
\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)-\mathbbm{E}(D_i|Z_i=0)} = 
\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} = \mathbbm{E}(Y_{i1} - Y_{i0}|C_i = 1)
\label{eq:ToT}
\end{equation}
since $\mathbbm{E}(D_i|Z_i=0)=0$ by \eqref{eq:potentialTreatments}.

@@

\begin{figure}[H]
    \caption{Effect of CATE benefit vs predicted take-up}
    \label{HTE_vs_propensity}
    \begin{center}
    \begin{subfigure}{0.475\textwidth}
        \caption{APR benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_apr.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Repayment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_des.pdf}
    \end{subfigure}
     \begin{subfigure}{0.475\textwidth}
        \caption{Default}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_def.pdf}
    \end{subfigure} 
    \end{center}
     \scriptsize   This figure asks whether it is the case that people with larger causal benefits from the Forced Commitment contract would be more likely to select that contract. To do this we proceed in two steps. First we estimate a flexible model of take-up of the commitment-fee contract \textit{in the choice arm} using gradient boosting classification, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$. We extrapolate this model to clients in the Forced Commitment arm to estimate what would they have chosen if we had given them choice. We plot $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins. The Y-axis plots the heterogeneous treatment effects of the (a) effective APR (in the positive scale) and (b) repayment, averaged for the respective x-axis bin. Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it. 
          %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
\end{figure}

@@

\begin{figure}[H]
    \caption{Negative selection on treatment effects}
    \label{benefit_vs_choice_cdf}
    \begin{center}
    \begin{subfigure}{0.475\textwidth}
        \caption{APR benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_apr.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Repayment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_des.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Default}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_def.pdf}
    \end{subfigure}
    \end{center}
     \scriptsize    CDF of the heterogeneous treatment effect for choosers vs non-choosers. The dotted line below indicates the points where the difference in the distributions is significant.  Instead of a single global null hypothesis (that the two CDFs are identical), there is a continuum of individual null hypotheses of CDF equality at each point. This methodology was proposed by \cite{GOLDMAN2018143}.
          %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
\end{figure}
